### 2019-10-05 thesis/txt/0-introduction.tex
filling various sections with points on what to write about
notes in various thesis parts

These build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or .. \mention{find more reasons}. Second, for reasearchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project. However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.

There are many different extraction techniques use for this task. Beller et al.  used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al. wrote a custom parser for Java Maven buildlogs to gather information for build repair hints \cite{vassallo2018un-break}. Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build.~\cite{amar2019mining} \bp{anecdotal: keyword search?}. Apart from those there are various more extraction techniques like searching for keywords, ... \todo{more?} \bp{problem which to choose}

@@

\begin{itemize}
  \item{RQ1:} Is Programming by Example suited to extract information from CI build logs?
  \item{RQ2:} What criteria influence the suitability of an information extraction technique for CI build logs?
  \item{RQ3:} When are text similarity or keyword search better suited for information extraction from CI build logs?
\end{itemize}

@@

\begin{itemize}
  \item A model to characterize information extraction techniques from \todo{CI?} build logs
  \item A model to characterize use case scenarios for information extraction from CI build logs
  \item A model of the extractable information in CI build logs
  \item A tool unifying several information extraction techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library,
          \item a common information retrieval approach using text similarity, and
          \item a simple keyword search approach
        \end{itemize}
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the extractions according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information extraction techniques \todo{not quite clear \emph{what} we evaluate here}
  \item A extendable model \todo{really? maybe scheme, decision tree} supporting decision on the three information extraction techniques relative to a given use case scenario
\end{itemize}

>>>>

These build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or .. \mention{find more reasons}. Second, for researchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project. However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.

There are many different extraction techniques use for this task. Beller et al.  used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints \cite{vassallo2018un-break}. Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build.~\cite{amar2019mining} \bp{anecdotal: keyword search?}. Apart from those there are various more extraction techniques like searching for keywords, ... \todo{more?} \bp{problem which to choose}

@@

\begin{itemize}
  \item[RQ1:] What criteria influence the suitability of an information extraction technique for CI build logs?
  \item[RQ2:] Is Programming by Example suited to extract information from CI build logs?
  \item[RQ3:] When are text similarity or keyword search better suited for information extraction from CI build logs?
\end{itemize}

@@

\begin{itemize}
  \item A model to characterize information extraction techniques from \todo{CI?} build logs
  \item A model to characterize use case scenarios for information extraction from CI build logs
  \item A model of the extractable information in CI build logs
  \item A tool unifying several information extraction techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library,
          \item a common information retrieval approach using text similarity, and
          \item a simple keyword search approach
        \end{itemize}
  \item Log Collector Tool
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the extractions according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information extraction techniques \todo{not quite clear \emph{what} we evaluate here}
  \item A extendable model \todo{really? maybe scheme, decision tree} supporting decision on the three information extraction techniques relative to a given use case scenario
\end{itemize}

### 2019-10-05 thesis/txt/3-data-set.tex
notes in various thesis parts

\section{Log Collector}
ghtorrent, travis, implementation description, reference CLI interface nicely?
describe special cases?
\todo{image! like in travistorrent paper}

\section{Collection Process}
differentiate original collection and for data set?
actual instantiation: 30 langs, 3 repos that use Travis, 10 failed logs each -> 80 useable, x logs
our impression?
\todo{image!}

\section{Labeling (better name?)}
  \subsection{Build Failure Reason}

>>>>

\section{Log Collector}
To collect a broad range of build logs we built the \texttt{Log Collector} using ruby.

  \subsection{Sampling Repositories}
  Our first task was to determine a set of repositories to query logs from. Our \texttt{GHTorrentParser} can query the GHTorrent dataset for the most popular languages on github and the most popular repositories for a given language. \emph{Popularity} in this case is defined as the number of watches. Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.

  \subsection{Sampling Builds}
  The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API, to obtain the newest builds for a given repository. As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state. We encountered the following states during our data collection passes:
  \begin{itemize}
    \item \todo{fill /5 mins/}
  \end{itemize}
  \texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.

  \subsection{Sampling Logs}
  For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
  A single build can consist of multiple jobs, e.g. building and executing tests in various different testing environments.
  \texttt{TravisRequester} therefore queries each build for a job, which has the same state.
  A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
  For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.

\todo{image! like in travistorrent paper, /draft 10 mins/}

\section{Collection Process}
For our inital data collection \emdash to get an impression of build logs from various projects and languages \emdash we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
our impression?
\todo{image!}

\section{Labeling (better name?)}
For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

  \subsection{Build Failure Reason}

### 2019-10-05 thesis/txt/4-tool.tex
notes in various thesis parts

\section{PROSE Program Synthesis}
implementation details :)
C#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

>>>>

\section{PROSE Program Synthesis}
implementation details :)
C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
